\documentclass[10pt]{article}
\usepackage{fancyhdr}
\usepackage{poemscol}
\usepackage{lmodern}

\begin{document}
\poemtitle{A Birthday Present}
\sequencetitle{Ariel}
\begin{poem}
  \begin{stanza}
    What is this, behind this veil, is it ugly, is it beautiful?\verseline
    It is shimmering, has it breasts, has it edges?
  \end{stanza}
  \begin{stanza}
    I am sure it is unique, I am sure it is what I want.\verseline
    When I am quiet at my cooking I feel it looking, I feel it thinking
  \end{stanza}
  \begin{stanza}
    'Is this the one I am to appear for,\verseline
    Is this the elect one, the one with black eye-pits and a scar?
  \end{stanza}
  \begin{stanza}
    Measuring the flour, cutting off the surplus,\verseline
    Adhering to rules, to rules, to rules.
  \end{stanza}
  \begin{stanza}
    Is this the one for the annunciation?\verseline
    My god, what a laugh!'
  \end{stanza}
  \begin{stanza}
    But it shimmers, it does not stop, and I think it wants me.\verseline
    I would not mind if it was bones, or a pearl button.
  \end{stanza}
  \begin{stanza}
    I do not want much of a present, anyway, this year.\verseline
    After all, I am alive only by accident.
  \end{stanza}
  \begin{stanza}
    I would have killed myself gladly that time any possible way.\verseline
    Now there are these veils, shimmering like curtains,
  \end{stanza}
  \begin{stanza}
    The diaphanous satins of a January window\verseline
    White as babies' bedding and glittering with dead breath. O ivory!
  \end{stanza}
  \begin{stanza}
    It must be a tusk there, a ghost-column.\verseline
    Can you not see I do not mind what it is.
  \end{stanza}
  \begin{stanza}
    Can you not give it to me?\verseline
    Do not be ashamed --- I do not mind if it is small.
  \end{stanza}
  \begin{stanza}
    Do not be mean, I am ready for enormity.\verseline
    Let us sit down to it, one on either side, admiring the gleam,
  \end{stanza}
  \begin{stanza}
    The glaze, the mirrory variety of it.\verseline
    Let us eat our last supper at it, like a hospital plate.
  \end{stanza}
  \begin{stanza}
    I know why you will not give it to me,\verseline
    You are terrified
  \end{stanza}
  \begin{stanza}
    The world will go up in a shriek, and your head with it,\verseline
    Bossed, brazen, an antique shield,
  \end{stanza}
  \begin{stanza}
    A marvel to your great-grandchildren.\verseline
    Do not be afraid, it is not so.
  \end{stanza}
  \begin{stanza}
    I will only take it and go aside quietly.\verseline
    You will not even hear me opening it, no paper crackle,
  \end{stanza}
  \begin{stanza}
    No falling ribbons, no scream at the end.\verseline
    I do not think you credit me with this discretion.
  \end{stanza}
  \begin{stanza}
    If you only knew how the veils were killing my days.\verseline
    To you they are only transparencies, clear air.
  \end{stanza}
  \begin{stanza}
    But my god, the clouds are like cotton ---\verseline
    Armies of them. They are carbon monoxide.
  \end{stanza}
  \begin{stanza}
    Sweetly, sweetly I breathe in,\verseline
    Filling my veins with invisibles, with the million
  \end{stanza}
  \begin{stanza}
    Probable motes that tick the years off my life.\verseline
    You are silver-suited for the occasion. O adding machine--
  \end{stanza}
  \begin{stanza}
    Is it impossible for you to let something go and have it go whole?\verseline
    Must you stamp each piece in purple,
  \end{stanza}
  \begin{stanza}
    Must you kill what you can?\verseline
    There is this one thing I want today, and only you can give it to me.
  \end{stanza}
  \begin{stanza}
    It stands at my window, big as the sky.\verseline
    It breathes from my sheets, the cold, dead center
  \end{stanza}
  \begin{stanza}
    Where spilt lives congeal and stiffen to history.\verseline
    Let it not come by the mail, finger by finger.
  \end{stanza}
  \begin{stanza}
    Let it not come by word of mouth, I should be sixty\verseline
    By the time the whole of it was delivered, and too numb to use it.
  \end{stanza}
  \begin{stanza}
    Only let down the veil, the veil, the veil.\verseline
    If it were death
  \end{stanza}
  \begin{stanza}
    I would admire the deep gravity of it, its timeless eyes.\verseline
    I would know you were serious.
  \end{stanza}
  \begin{stanza}
    There would be a nobility then, there would be a birthday.\verseline
    And the knife not carve, but enter
  \end{stanza}
  \begin{stanza}
    Pure and clean as the cry of a baby\verseline
    And the universe slide from my side.
  \end{stanza}
\end{poem}
\end{document}
